\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-12 paper.tex
added some analytical results

Secondly, we see that the software library that comes with the generated code
adds to the size of the resulting image. But the cost is close to constant and
is lower for both algorithms together. With roughly 3KB of additional overhead,
or 15\% in this simple case, this impact limited.

@@

>>>>

Secondly, we see that the software library that comes with the generated code
adds to the size of the resulting image. But the cost is close to constant and
is lower for both algorithms together. With roughly 3KB of additional overhead,
or 15\% in this simple case, the impact is small. Taking into account the
available memory on the ATMega1284p, this is merely 2.3\% of the available
resources.

@@

\subsection{Analytical Results}

Looking at the generated source code is another way to validate the framework.
Reusing common data allows elimination of for example the network address
within the scope of each individual algorithm. Analysis of the source code with
both algorithms implemented, shows that this reduces the memory footprint for
one node with 2 bytes from 27 bytes to 25 bytes. A ZigBee network address
indeed consists of 16 bits. So this results in a reduction of 7.4\%. Using
ZigBee's 64 bits unique addresses, this reduction can easily become 20.5\%.

Finally comparing the amount of code versus the size of the formal description
of IDS algorithms, can be an indication of the development effort. Implementing
both algorithms manually results in 637 lines of clean and documented C code.
The corresponding \NAME implementation results in 156 lines of DSL code.
